%\documentclass{article}
%\usepackage[
%    left=1.2in,
%    right=1.2in,
%    top=0.4in,
%    bottom=0.7in,
%    paperheight=11in,
%    paperwidth=8.5in
%]{geometry}

%\usepackage{layout}
\clearpage
\mytitle{Interoperable Private Attribution: A Distributed Attribution and Aggregation Protocol \large \\Paper Summary}
%\renewcommand{\title}{TVA: A multi-party computation system for secure and expressive time series analytics \large \\Paper Summary}
%\author{Sandhya Saravanan\\
%  \small MSR, India\\\\
%}
%\date{\vspace{-5ex}}

%\begin{document}
%\maketitle
\setcounter{section}{0} % Restart section numbering

\section{Context Setting}
\subsection{Terms}
\underline{Ad impression}: Action - Ad interaction such as a view/click by user on publisher website \\

\underline{Ad conversion}: Action - Purchase/Newletter signup by user on advertiser website \\

\subsection{Schema}
Consider a Publisher that owns the Ad Impressions Database whose schema is as follows:
\begin{enumerate}
    \item I\_Timestamp
    \item I\_PublisherID
    \item I\_AdvertiserID
    \item I\_UserID
    \item I\_Metadata (Click/View, Ad size)
\end{enumerate}

Consider an Advertiser that owns the Ad Conversions Database whose schema is as follows:
\begin{enumerate}
    \item C\_Timestamp
    \item C\_AdvertiserID
    \item C\_UserID
    \item C\_Metadata (Sign up/Purchase, Purchase value)
\end{enumerate}

\subsection{Supported Functionality}
\begin{enumerate}
    \item Attribution: Assign an ad conversion to one or more impressions based on a fixed attribution rule. E.g. Last Touch Attribution (LTA), First Touch Attribution (FTA), Uniform Attribution, Time Decay Attribution
    \item Queries on Resulting Attributed Dataset 
\end{enumerate}

\section{Summary}


\subsection{Supported Functionality}
\begin{enumerate}
    \item Last Touch Attribution: Assigns an ad conversion to an ad impression with the closest preceding timestamp and same User ID 
    \item SUM (conversion value from conversion metadata) GROUP BY (impression value from impression metadata)
\end{enumerate}

\subsection{Schema}
Ad impression and ad conversion have same schema:
\begin{enumerate}
    \item Timestamp
    \item UserID
    \item Impression/Conversion (0 for Impression, 1 for Conversion)
    \item Metadata (Click/View, Ad size)
    \begin{itemize}
        \item Aggregation Category
        \item Purchase Value
    \end{itemize}
\end{enumerate}

\subsection{Limitations}
Only one-to-many and many-to-one relationship between Publisher and Advertiser is supported i.e. 1 publisher can host ads from many advertisers or 1 advertiser can host their ads across many publishers. The case of many publishers hosting ads from many advertisers is not considered, although it is feasible. Reason seems related to the way Differential Privacy technique is used.

\subsection{Setting}
Report Collector (RC) collects impression and conversion events and batches them / unions them into a single database. Report Collector has access to all data except UserID in clear. First, they sort by Timestamp. Then, they create replicated secret shares and distribute to 3 parties. \\

Attribution and aggregation are done by 3PC MPC (Malicious abort, Honest Majority, 1 corruption)

\subsection{MPC Stages and Costs}
Let n be number of rows, and m be number of attributes in the dataset. Let $|$UserID$|$ represent bit length of the UserID attribute (maximum no. of bits required to represent a UserID).

\begin{enumerate}
    \item Verify that shares are well formed i.e. sharing of the dataset values is correct
    \begin{itemize}
        \item Communication: 3mnl bits (we take l to be the ring size taken for sharing)
        \item Rounds: 1
    \end{itemize}
    \item Stable Radix sort by User ID
    \begin{itemize}
        \item Communication: $O(|$UserID$|n\log n)$ bits
        \item Rounds: $O(|$UserID$|)$
    \end{itemize}
    \item Oblivious Last Touch Attribution (Similar to GroupMax protocol in our DT Training protocol)
    \begin{itemize}
        \item Communication: $3n\log n c_{mult}$ bits
        \item Rounds: $O(\log n)$
    \end{itemize}
    \item Secure Aggregation 
    \begin{itemize}
        \item Communication: $O(nk)c_{eq}$ bits (where k is the no. of aggregation categories) 
        \item Rounds: $r_{eq}$
    \end{itemize}
\end{enumerate}

\subsection{Technique (as provided in paper)}
\begin{enumerate}
   \item Local Decryption: Parties decrypt the shares of match key they were sent encrypted under their public key.
   \item Verify: Parties ensure there is DP budget available for RC submitting query (To prevent leakage of info about people over time which can happen with any system that reveals aggregate measurements about people). Parties also ensure that query is a well formed source fan out or trigger fan out query (Run verification protocol).
   \item Parties compute stable sort (radix sort) by value of match keys. Each match key's reports are sorted by timestamp. 
   \item Last touch attribution: Assigns credit for a trigger report's value to first source report that occurred early in time with same match key (Parallel prefix sum from GraphSC approach)
   \item Capping: Computes total contribution of each person to measurement result across all breakdowns (histogram buckets). If this contribution exceeds per-person cap, we drop their contribution down to cap.
   \item Aggregation: Sums attributed trigger values into separate histogram buckets according to breakdown key of source report they were attributed to.
   \item DP Noise Addition: Apply DP noise to aggregate for each breakdown and reveal result to RC who submitted query. 
\end{enumerate}

\subsection{Claim to Fame}
\begin{enumerate}
    \item Private join is not used unlike in previous works. Model where inputs come from multiple client devices rather than just 2 parties is supported.
    \item Malicious security
    \item Apple's Private Click Measurement uses heuristics to reduce linkage of attributed reports to individuals
    \item Google's "Attribution Reporting API with Agregate Reports" uses a Trusted Execution Environment as the server side aggregation system.
\end{enumerate}

% Bibliography
%-----------------------------------------------------------------
%\begin{thebibliography}{99}

%\bibitem{TVA22} Muhammad Faisal, Boston University; Jerry Zhang \emph{TVA: A multi-party computation system for secure and expressive time series analytics}, {USENIX} (2023)

%\end{thebibliography}

%\end{document}
