%\documentclass{article}
%\usepackage[
%    left=1.2in,
%    right=1.2in,
%    top=0.4in,
%    bottom=0.7in,
%    paperheight=11in,
%    paperwidth=8.5in
%]{geometry}

%\usepackage{layout}
\clearpage
\mytitle{Constant-Round Private Decision Tree Evaluation for Secret Shared Data \large \\Paper Summary}
%\renewcommand{\title}{TVA: A multi-party computation system for secure and expressive time series analytics \large \\Paper Summary}
%\author{Sandhya Saravanan\\
%  \small MSR, India\\\\
%}
%\date{\vspace{-5ex}}

%\begin{document}
%\maketitle
\setcounter{section}{0} % Restart section numbering

\section{Summary}

\subsection{Setting}
\begin{enumerate}
    \item 3 servers
    \item Service provider (tree owner) has the trained DT model. It generates and distributes 3P shares of the tree to the 3 servers.
    \item Client (can be many clients for many evaluations) with an attribute vector as input. It generates and distributes 3P shares to 3 servers.
    \item (2, 3) RSS, Semi honest security, honest majority (only 1 out of 3 corruptions permitted)
\end{enumerate}

\subsection{Results}
\begin{enumerate}
    \item 5 round online phase
\end{enumerate}

\subsection{Decision Tree Representation}
Consider a complete binary tree with height $h$, size of an attribute vector $m$. 

Internal Node:
\begin{enumerate}
    \item (i, j) where i represents level number (ranges from 0 to h-1) and j represents position within a level (ranges from 0 to $2^i - 1$.
    \item cond = 0 (equality check) or 1 (less than) 
    \item attribute index (replicated secret shared over m-bit ring)
    \item threshold (replicated secret shared over k-bit ring)
\end{enumerate}

Leaf Node:
\begin{enumerate}
    \item Leaf no. i (ranges from 0 to $2^h - 1$) 
    \item value v (replicated secret shared over k bit ring)
\end{enumerate}

\subsection{Protocol Overview}
\begin{enumerate}
    \item Feature Selection (Offline: $10mk(2^h - 1)$ bits, 2 rounds, Online: $(4mk + 3\log m)(2^h - 1)$ bits, 1 round)
    \begin{itemize}
        \item i/p: Share of index (idx), Shared attribute m-length vector (x)
        \item o/p: Share of attribute corresponding to index (1 k-bit ring element)
        \item Approach:
        \begin{itemize}
            \item Oblivious circular shift of $x$ by randomness $\eta$, call it $y$.
            \item $s = idx + \eta$ and reveal $s$
            \item Output $y_s$
        \end{itemize}
    \end{itemize}
    \item Comparison (Offline: $(2(\lambda+7)(k+1) - 5)(2^h - 1)$ bits, Online: $(4k+13)(2^h - 1)$ bits, 2 rounds)
    \begin{itemize}
        \item Share conversion (for selected attribute and threshold): (3, 2) RSS to (2, 2) additive shares
        \item Compute in parallel: a = LT(Selected attribute, Threshold), b = EQ(Selected attribute, Threshold) in parallel (1 round).
        \item Compute $b \oplus \text{SC-AND}(cond, a \oplus b$. SC-AND to evaluate AND gate and share conversion at the same time.
        \item Convert above back to (3, 2) RSS.
    \end{itemize}
    \item Path Evaluation (Offline: $4(2^h - 1)$ bits, 2 rounds, Online: $5k.2^h + 4(2^h - 1)$, 2 rounds)
    \begin{itemize}
        \item i/p: Shares of $2^h - 1$ leaf values, shares of comparison results at every inner node
        \item o/p: Shares of value associated with corresponding leaf node indicated by comparison results
        \item Idea: Oblivious tree shuffle - Shuffle a shared tree obliviously while sustaining tree structure. Then, reveal the shuffled node values, detect the right trace path while leaking no info on i/p tree.
        \item Suppose $c$ is the complete binary tree until depth $h-1$, which consists of just 0s and 1s representing results of comparisons on the internal nodes.
        \item Let $r$ be a complete binary tree until depth $h-1$ with 0s and 1s randomly sampled. Consider that permutation $\pi_r$ is calculated in a special way from $r$.
        \item Let $v$ represent the vector of leaf values.
        \item $(c, v).r = (c \circ r, v . \pi_r)$ and $c \circ r = (c . \pi_r) \oplus r = (c \oplus r.\pi_r^{-1}).\pi_r$ 
    \end{itemize}
\end{enumerate}

%
%\begin{table}
%        \centering
%        \begin{tabularx}{\textwidth}{ |X|X|X| }
%                \hline
%                \textbf{Comparison point} & \textbf{IPA} & \textbf{PAM} \\ \hline
%                \textbf{Attribution} & Server-side  & On-Device \\ \hline
%                \textbf{Communication cost (e.g. measured via no. of bits sent by helper servers)} & High (Attribution logic performed using SMPC) & Low (Addition doesn't require communication between Prio nodes during computation)  \\ \hline
%        \end{tabularx}
%\end{table}

\subsection{Limitations}
\begin{enumerate}
    \item Semi-honest security
    \item Operation at inner node limited to LT and EQ.
    \item We deal with complete binary tree.
\end{enumerate}

% Bibliography
%-----------------------------------------------------------------
%\begin{thebibliography}{99}

%\bibitem{TVA22} Muhammad Faisal, Boston University; Jerry Zhang \emph{TVA: A multi-party computation system for secure and expressive time series analytics}, {USENIX} (2023)

%\end{thebibliography}

%\end{document}
