%\documentclass{article}
%\usepackage[
%    left=1.2in,
%    right=1.2in,
%    top=0.4in,
%    bottom=0.7in,
%    paperheight=11in,
%    paperwidth=8.5in
%]{geometry}

%\usepackage{layout}
\clearpage
\mytitle{Interoperable Private Attribution: A Distributed Attribution and Aggregation Protocol \large \\Paper Summary}
%\renewcommand{\title}{TVA: A multi-party computation system for secure and expressive time series analytics \large \\Paper Summary}
%\author{Sandhya Saravanan\\
%  \small MSR, India\\\\
%}
%\date{\vspace{-5ex}}

%\begin{document}
%\maketitle
\setcounter{section}{0} % Restart section numbering

\section{Summary}
\subsection{Terms}
\begin{enumerate}
    \item Ad impression: No. of times an ad was displayed
    \item Ad click: No. of times ad was clicked on
    \item Ad conversion: No. of desired actions (goals) performed by user (e.g. filling in a contact form or making a purchase)
    \item Source event: Refers to an ad impression
    \item Trigger event: Refers to an ad conversion
    \item Report: Collection of data associated with an event
    \item Attribution measurement: Query over a set of source reports and trigger reports
    \item Source fanout query:
    \begin{itemize}
        \item Helps a website/app understand the effect that the ads it shows have on outcomes for its advertisers.
        \item Can only contain source reports from a single source website/app and trigger reports from multiple sites where each report might represent a conversion event
    \end{itemize}
    \item Trigger fanout query:
    \begin{itemize}
        \item Helps a site that buys ads to understand how its advertising is helping to drive outcomes on its website/app
        \item Can only contain trigger reports from a single trigger website/app and source reports from multiple sites where each report might represent an ad impression or click
    \end{itemize}
    \item Report Collector: Collects a batch of source and trigger reports into a source fan-out or trigger fan-out query
    \item Match key: Unique identifier for each person
\end{enumerate}

\subsection{Technique}
\underline{Security Model}: 3-party, malicious, honest majority MPC \\

\begin{enumerate}
   \item Local Decryption: Parties decrypt the shares of match key they were sent encrypted under their public key.
   \item Verify: Parties ensure there is DP budget available for RC submitting query (To prevent leakage of info about people over time which can happen with any system that reveals aggregate measurements about people). Parties also ensure that query is a well formed source fan out or trigger fan out query (Run verification protocol).
   \item Parties compute stable sort (radix sort) by value of match keys. Each match key's reports are sorted by timestamp. 
   \item Last touch attribution: Assigns credit for a trigger report's value to first source report that occurred early in time with same match key (Parallel prefix sum from GraphSC approach)
   \item Capping: Computes total contribution of each person to measurement result across all breakdowns (histogram buckets). If this contribution exceeds per-person cap, we drop their contribution down to cap.
   \item Aggregation: Sums attributed trigger values into separate histogram buckets according to breakdown key of source report they were attributed to.
   \item DP Noise Addition: Apply DP noise to aggregate for each breakdown and reveal result to RC who submitted query. 
\end{enumerate}

% Bibliography
%-----------------------------------------------------------------
%\begin{thebibliography}{99}

%\bibitem{TVA22} Muhammad Faisal, Boston University; Jerry Zhang \emph{TVA: A multi-party computation system for secure and expressive time series analytics}, {USENIX} (2023)

%\end{thebibliography}

%\end{document}
