%\documentclass{article}
%\usepackage[
%    left=1.2in,
%    right=1.2in,
%    top=0.4in,
%    bottom=0.7in,
%    paperheight=11in,
%    paperwidth=8.5in
%]{geometry}

%\usepackage{layout}
\clearpage
\mytitle{Privacy-preserving edit distance computation using secret-sharing two-party computation \large \\Paper Summary}
%\renewcommand{\title}{TVA: A multi-party computation system for secure and expressive time series analytics \large \\Paper Summary}
%\author{Sandhya Saravanan\\
%  \small MSR, India\\\\
%}
%\date{\vspace{-5ex}}

%\begin{document}
%\maketitle
\setcounter{section}{0} % Restart section numbering

\section{Summary}
\underline{Problem Statement}: Alice and Bob each has a DNA chain represented as a list of nucleotides (A, T, C, G). They want to compare edit distance of both chains, but without revealing their chain to each other.\\

\underline{Cleartext solution}: Wagner-Fischer algorithm (Dynamic Programming) \\

Given a string A of length n, and string B of length m, we want to find edit distance d(A, B). So for $1 \le i \le n$ and $1 \le j \le m$ \\

$D(i, j) = min ( D(i-1, j) + 1, D(i, j-1) + 1, D(i-1, j-1) + t(i, j))$ \\

with $t(i, j) = 1$ if $a_i \neq b_j$ and $0$ otherwise.\\

\underline{Technique}
\begin{enumerate}
   \item 2PC MPC Protocol
    \item Nucleotides encoded using binary representation 
    \item Tinier used to compute equality test between pair of nucleotides in $Z_2$ 
    \item Equality results are in the form of binary shares. Converted to arithmetic shares using daBits 
    \item Communication: $mnc_{eq}$ + $mnc_{B2A}$ bits 
    \item Comparison done using edaBits 
    \item Secure min uses MIN\textsubscript{q}: Min. of a list of q numbers computed with communication $(2q-2)c_{mult} + (q-1)c_{comp}$ in $O(\log q)(r_{comp}+2)$ rounds
    \item Blocker: Sequential nature of computation. Blows up no. of rounds
    \item To bring down no. of rounds, this paper divides D into sub matrices of $\tau$ x $\tau$ and expands the recursive formulae (exact method described in paper using graph theory techniques). This brings down no. of rounds by $\tau$ but increases number of multiplications and comparisons, thereby increasing communication. This is because number of formulas in the min computation is $O(\tau 2^{3\tau})$
    \begin{description}
        \item[Communication: $O((nm/\tau ^2)(\tau ^22^{3\tau}-\tau))c_{comp} + O((nm/\tau ^2)(\tau ^22^{3\tau + 1}-2\tau))c_{mult}$]
        \item[Rounds: $O((nm/\tau ^2)(3\tau + \log \tau)(r_{comp}+2))$ ]
    \end{description}
\end{enumerate}

% Bibliography
%-----------------------------------------------------------------
%\begin{thebibliography}{99}

%\bibitem{TVA22} Muhammad Faisal, Boston University; Jerry Zhang \emph{TVA: A multi-party computation system for secure and expressive time series analytics}, {USENIX} (2023)

%\end{thebibliography}

%\end{document}
