%\documentclass{article}
%\usepackage[
%    left=1.2in,
%    right=1.2in,
%    top=0.4in,
%    bottom=0.7in,
%    paperheight=11in,
%    paperwidth=8.5in
%]{geometry}

%\usepackage{layout}
\clearpage
\mytitle{Lightweight, Maliciously Secure Verifiable Function Secret Sharing  \large \\Paper Summary}
%\renewcommand{\title}{TVA: A multi-party computation system for secure and expressive time series analytics \large \\Paper Summary}
%\author{Sandhya Saravanan\\
%  \small MSR, India\\\\
%}
%\date{\vspace{-5ex}}

%\begin{document}
%\maketitle
\setcounter{section}{0} % Restart section numbering

\section{Contributions}
\begin{enumerate}
    \item Verifiable FSS for point functions
    \item Verifiable FSS for multi-point functions
\end{enumerate}

Independent of output group size, structure of DPF output, set of points on which DPF must be evaluated. \\

\subsection{Security Model}
\begin{enumerate}
    \item 2P, no collusion
    \item If client deviates from protocol, SH servers detect misbehaviour
    \item If one of the servers is corrupted, client's privacy is maintained. 
\end{enumerate}

Works compared with: BGI16, Poplar \\

\subsection{Starting Point: Verifying Zero Function}
Consider 2 servers $S_0$ and $S_1$ that have shares of $\bar{y}$ i.e. $S_0$ has $[\bar{y}]_0$ and $S_1$ has $[\bar{y}]_1 = -[\bar{y}]_0$. Now, $S_1$ negates its share i.e. $S_1$ now holds $[\bar{y}]_0$. $S_0$ and $S_1$ now have identical vectors. To check, hash to $2\lambda$ bits and exchange them.

\subsection{BGI16 Construction}
Let $y$ be the length-N vector obtained on EvalAll of DPF key ($\beta=0/1$). Let $y_0$ and $y_1$ be the shares of $y$. Consider a 3xN matrix, each column j of L defined to be $L_{1, j} = r_j$, $L_{2, j} = s_j$ and $L_{3, j} = r_j.s_j$ where $r_j, s_j$ are sampled uniformly at random over $\mathbb{F}$. \\

Key idea: $L.y_b = z_b$ where $z_b$ is a secret sharing of $(z_1, z_2, z_3)$. \\

$S_0$ and $S_1$ check if $z_3 = z_1.z_2$ using MPC. Probability that this check passes if $y$ is not the non-zero vector of unit vector is at most $2/\mathbb{F}$. For security parameter $\lambda$, $\mathbb{F}$ must be at least $2^{\lambda+1}$.

\subsection{Drawbacks of BGI16 Construction}
Consider general $\beta$ (value at special point) i.e. $\beta \neq \beta^2$. Our final MPC check is now for $\beta.z_3 = z_1.z_2$. Client provides secret sharing of $\beta$ to compute this. This construction is vulnerable to additive attacks.

\subsubsection{Additive Attack (Malicious Server case)}
Consider that a malicious server adds $\Delta$ to $z_3$. This can be done by adding $\Delta$ to a share of $z_3$. Also consider that the server adds $3\Delta$ to $z_1.z_2$ i.e. to a share of the output of multiplication gate with inputs $z_1$ and $z_2$. If $\beta.(z_3+\Delta) \neq z_1.z_2 + 3\Delta$, servers can conclude that $\beta \neq 3$. 

\subsection{Poplar Construction}
To solve the additive attacks problem in BGI16, Poplar does the following.

Let $y$ be the length-N vector obtained on EvalAll of DPF key. $y$ has value $\beta$ at special point. Let $y^*$ be the length-N vector that has value $k.\beta$ at special point.

Let $y_0$, $y_1$ be the shares of $y$ and $y^*_0$, $y^*_1$ be the shares of $y^*$. Let $r = (r_1, r_2, ..., r_N)$ be an N-length vector with each element $r_i$ is sampled uniformly at random from $\mathbb{F}$. Let $r^* = (r_1^2, ..., r_N^2)$. \\

Let $z_b = \langle r, y_b \rangle$. $z_b^* = \langle r^*, y_b \rangle$. $z_b^{**} = \langle r, y_b^* \rangle$.

Servers use secure computation to check: $(z^2 - z^*) + (k.z - z^{**})$.

\subsection{Drawbacks of Poplar Construction}

If an additive shift is applied to $k$ and the verification still passes, the attacker can conclude that $\beta$ and $k.\beta$ are both 0. To overcome this, $k$ value is embdedded in an OLE correlation.

\section{Technique Overview for Point Function}

Suppose $S_0$ holds $[\bar{y}]_0$ and $S_1$ holds $[\bar{y}_1]$ which are shares of $[0, 0, \beta, ..., 0]$. \\

Let $S_0$ and $S_1$ have a correction word $\omega = [\beta]_0 + [\beta]_1$ along with their respective keys. We want the following correction functionality:\\

\noindent correct($[0]_0, \omega$) = correct($[0]_1, \omega$) \\
correct($[\beta]_0, \omega$) = correct($[\beta]_1, \omega$) \\
correct($[\tilde{\beta}]_0, \omega$) $\neq$ correct($[\tilde{\beta}]_1, \omega$) where $\beta \neq \tilde{\beta} \neq 0$ \\

Consider we have $t_0^{(*)} \neq t_1^{(*)}$ and $t_0^{(i)} = t_1^{(i)}$ \\

For $S_0$: \\
$[0]_0 \oplus (t_0^{(i)}.\omega) = v_i$ \\
$[\beta]_0 \oplus (t_0^{(*)}.\omega) = v_*$ \\

For $S_1$: \\
$[0]_1 \oplus (t_1^{(i)}.\omega) = v_i$ \\
$[\beta]_1 \oplus (t_1^{(*)}.\omega) = v_*$ \\

Correction operation is as follows:
\begin{enumerate}
    \item Input is a share $u = [y]_b$. If $b = 1$, set $u \leftarrow -u$
    \item Hash $u$ to get $v = H(u)$
    \item If LSB of $v$ is 1, output $v \oplus w$, else output $v$.
\end{enumerate}

Guarantees
\begin{enumerate}
    \item If inputs are shares of 0, outputs are equal.
    \item Client samples keys until $LSB(H[\beta]_0) \neq LSB(H[\beta]_1)$.
    \item If inputs are shares of $\beta$, outputs are equal.
    \item If malicious client corrects $> 1$ error, they've found inputs $u_1 \neq u_2$ and $u_3 \neq u_4$ s.t. $\omega = H(u_1) \oplus H(u_2) = H(u_3) \oplus H(u_4)$
\end{enumerate}

\section{Technique Overview for Multi-point Function}
\underline{Idea}: If there are $t$ non-zero points, a multi-point function = Sum of t point functions i.e. Eval must evaluate $t$ DPF shares for each input, even though only 1 share will evaluate to a non-zero value.\\

Consider $m$ buckets, $k$ hash functions $h_1, ..., h_k$ which output $\{1, ..., m\}$. Each special point $\alpha$ from $\{\alpha_1, ..., \alpha_t\}$ is at an index $i = h_j(\alpha)$ for some $1 \leq j \leq k$.\\

Empty bucket holds a DPF sharing of zero function. Buckets that hold an index $\alpha_i$ hold a DPF sharing of $f_{\alpha_i, \beta_i}$. Therefore, we have $m$ DPF shares sent to server.\\

To evaluate $x$, we obtain indices $i_1, i_2, ..., i_k$ from $h_1(x), h_2(x), ..., h_k(x)$ and evaluate $k$ DPFs at buckets $i_1, ..., i_k$ and sum them up. ($m \leq 2t$)
%\end{document}
